**Density Dependence**

### 2023-03-07 Rmd/mseMac.Rmd
both aligned

```{r, omCheck}
om=fwdWindow(window(om,end=2020),end=2080,eqM)
f =FLQuant(rep(seq(0,c(refpts(eq)["crash","harvest"])*1.5,length.out=100),each=61),
           dimnames=dimnames(fbar(om)[,ac(2020:2080)]))
om=fwd(om,fbar=f,sr=eqM)

oms=FLStocks("Base"     =om)
oms[["DD Mass"]]        =om
oms[["DD Mass, Mat"]]   =om
oms[["DD Mass, Mat, M"]]=om
for (iYear in ac(2020:2080)){
  oms[["DD Mass"]]=ddFn(iYear,oms[["DD Mass"]],params,TRUE,FALSE,FALSE)
  oms[["DD Mass"]]=fwd(oms[["DD Mass"]],fbar=f[,iYear],sr=eqM)

  oms[["DD Mass, Mat"]]=ddFn(iYear,oms[["DD Mass, Mat"]],params,TRUE,TRUE,FALSE)
  oms[["DD Mass, Mat"]]=fwd(oms[["DD Mass, Mat"]],fbar=f[,iYear],sr=eqM)

  oms[["DD Mass, Mat, M"]]=ddFn(iYear,oms[["DD Mass, Mat, M"]],params,TRUE,TRUE,TRUE)
  oms[["DD Mass, Mat, M"]]=fwd(oms[["DD Mass, Mat, M"]],fbar=f[,iYear],sr=eqM)
  } 
```

@@

om=fwdWindow(window(iter(om,51),end=2020),end=2080,eqM)
F =propagate(fbar(om[,ac(2020:2080)]),4)
F[]=rep(rfpts$Fmsy,each=61)
control=as(FLQuants("f"=F),"fwdControl")

om =fwd(om,control=control,sr=eqM)

prj=FLStocks("Base"     =om)
prj[["DD Mass"]]        =om
prj[["DD Mass, Mat"]]   =om
prj[["DD Mass, Mat, M"]]=om
for (i in ac(2020:2080)) {
    prj[[2]] =ddFn(i,prj[[2]],params,massFlag=TRUE,matFlag=FALSE,mFlag=FALSE)
    control=as(FLQuants("f"=F[,i]),"fwdControl")
    prj[[2]] =fwd(prj[[2]],control=control,sr=eqM)

@@

@@

```{r, projectons-save}
save(prjs,file=paste(dirRuns,"/",stock,"Prjs.RData",sep=""))
```

@@

>>>>

```{r, omCheck}
om=fwdWindow(window(om,end=2020),end=2080,eqM)
F    =rep(c(seq(0,                                  c(refpts(eqM)["msy",  "harvest"]),  length.out=51),
            seq(c(refpts(eqM)["msy",  "harvest"]),c(refpts(eqM)["crash","harvest"])*1.5,length.out=51)[-1]))
F    =FLQuant(rep(F,each=61),dimnames=list(year=2020:2080,iter=seq(101)))
om=fwd(om,fbar=F,sr=eqM)

oms=FLStocks("Base"     =om)
oms[["DD Mass"]]        =om
oms[["DD Mass, Mat"]]   =om
oms[["DD Mass, Mat, M"]]=om
for (iYear in ac(2020:2080)){
  oms[["DD Mass"]]=ddFn(iYear,oms[["DD Mass"]],params,TRUE,FALSE,FALSE)
  oms[["DD Mass"]]=fwd(oms[["DD Mass"]],fbar=F[,iYear],sr=eqM)

  oms[["DD Mass, Mat"]]=ddFn(iYear,oms[["DD Mass, Mat"]],params,TRUE,TRUE,FALSE)
  oms[["DD Mass, Mat"]]=fwd(oms[["DD Mass, Mat"]],fbar=F[,iYear],sr=eqM)

  oms[["DD Mass, Mat, M"]]=ddFn(iYear,oms[["DD Mass, Mat, M"]],params,TRUE,TRUE,TRUE)
  oms[["DD Mass, Mat, M"]]=fwd(oms[["DD Mass, Mat, M"]],fbar=F[,iYear],sr=eqM)
  } 
```

@@

omFmsy=fwdWindow(window(iter(om,51),end=2020),end=2080,eqM)
F =propagate(fbar(omFmsy[,ac(2020:2080)]),4)
F[]=rep(rfpts$Fmsy,each=61)
control=as(FLQuants("f"=F),"fwdControl")

omFmsy =fwd(omFmsy,control=control,sr=eqM)

prj=FLStocks("Base"     =omFmsy)
prj[["DD Mass"]]        =omFmsy
prj[["DD Mass, Mat"]]   =omFmsy
prj[["DD Mass, Mat, M"]]=omFmsy
for (i in ac(2020:2080)) {
    prj[[2]] =ddFn(i,prj[[2]],params,massFlag=TRUE,matFlag=FALSE,mFlag=FALSE)
    control=as(FLQuants("f"=F[,i]),"fwdControl")
    prj[[2]] =fwd(prj[[2]],control=control,sr=eqM)

@@

```{r}
om.  =om
oms. =oms
prj. =prj
prjs.=prjs   
save(eqM,    file="~/Desktop/tmp/eqM.RData")
save(om.,    file="~/Desktop/tmp/om..RData")
save(omFmsy, file="~/Desktop/tmp/omFmsy.RData")
save(oms.,   file="~/Desktop/tmp/oms..RData")
save(prj.,   file="~/Desktop/tmp/prj..RData")
save(prjs.,  file="~/Desktop/tmp/prjs..RData") 
```

@@

@@

```{r, eval=FALSE}
load("~/Desktop/tmp/eqM.RData")
load("~/Desktop/tmp/om..RData")
load("~/Desktop/tmp/oms..RData")
load("~/Desktop/tmp/prj..RData")
load("~/Desktop/tmp/prjs..RData")

plot(FLStocks("mse"=om.,"report"=om))

refpts(vpaM_eq)
refpts(eqM)

plot(eqM)
plot(vpaM_eq)

plot(vpaM_eq)
```
